### 2016-08-17 rebuttal.tex

The authors

\pagebreak

\section{Comments from Editor}

\begin{questions}
\question I found the \url{http://live.sympy.org/} site very convenient for trying things
out in SymPy, but it is only mentioned in the supplement, which might be
overlooked by readers. I suggest moving that section into the main paper, as
it provides a great way to play along with the examples while reading the
paper.
\begin{solution}
This sentence was added to the introduction:
\begin{quote}
All examples could be tested on the \href{http://live.sympy.org}{SymPy
Live} instance, that is an online Python shell, which uses the Google
App Engine to execute SymPy code.
\end{quote}
\end{solution}
\question The Basic Usage section omits what I think is an important point:
how does one distinguish between evaluating exp(1) in Python and exp(1) in
SymPy? In other words, how are symbolic constants specified?
\begin{solution}
It's unclear what you are asking for.  Both Python standard library
and SymPy have exp callable, so it depends which symbols are
imported in your global namespace: the \texttt{exp} function from the \texttt{math}
module or \texttt{exp} class from SymPy.  In the later case a special
symbolic constant will be produced.

We have added a sentence to the section 2.2, that shows symbolic
constants as an example of leaf nodes:
\begin{quote}
Symbols or symbolic constants, like $e$ or $\pi$, are other examples of
leaf nodes.
\begin{verbatim}
>>> exp(1)
E
>>> exp(1).args
()
>>> x.args
()
\end{verbatim}
\end{quote}
\end{solution}
\question The first
thing I tried after seeing Table 2 (simplication functions) did not work:

@@

Emphasize that the environment variable \texttt{SYMPY\_DEBUG} must be set before importing SymPy for the first time.
\begin{solution}
Footnote was added right before the final example from the Gruntz algorithm section.
\end{solution}

### 2016-08-17 rebuttal.tex

The authors

\pagebreak

\section{Comments from Editor}

\begin{questions}
\question I found the \url{http://live.sympy.org/} site very convenient for trying things
out in SymPy, but it is only mentioned in the supplement, which might be
overlooked by readers. I suggest moving that section into the main paper, as
it provides a great way to play along with the examples while reading the
paper.
\begin{solution}
This sentence was added to the introduction:
\begin{quote}
All examples could be tested on the \href{http://live.sympy.org}{SymPy
Live} instance, that is an online Python shell, which uses the Google
App Engine to execute SymPy code.
\end{quote}
\end{solution}
\question The Basic Usage section omits what I think is an important point:
how does one distinguish between evaluating exp(1) in Python and exp(1) in
SymPy? In other words, how are symbolic constants specified?
\begin{solution}
It's unclear what you are asking for.  Both Python standard library
and SymPy have exp callable, so it depends which symbols are
imported in your global namespace: the \texttt{exp} function from the \texttt{math}
module or the \texttt{exp} class from SymPy.  In the later case a special
symbolic constant will be produced.

### 2016-08-17 rebuttal.tex

\section{Comments from Editor}

\begin{questions}
\question I found the \url{http://live.sympy.org/} site very convenient for trying things
out in SymPy, but it is only mentioned in the supplement, which might be
overlooked by readers. I suggest moving that section into the main paper, as
it provides a great way to play along with the examples while reading the
paper.
\begin{solution}
This sentence was added to the introduction:
\begin{quote}
All examples could be tested on the \href{http://live.sympy.org}{SymPy
Live} instance, that is an online Python shell, which uses the Google
App Engine to execute SymPy code.
\end{quote}
\end{solution}
\question The Basic Usage section omits what I think is an important point:
how does one distinguish between evaluating exp(1) in Python and exp(1) in
SymPy? In other words, how are symbolic constants specified?
\begin{solution}
  It's unclear what you are asking for. Both Python standard library and SymPy
  have exp callable, so it depends which symbols are imported in your global
  namespace: the \texttt{exp} function from the \texttt{math} module or the
  \texttt{exp} class from SymPy. In the later case a special symbolic constant
  will be produced.

We have added a sentence to the section 2.2, that shows symbolic
constants as an example of leaf nodes:
\begin{quote}
Symbols or symbolic constants, like $e$ or $\pi$, are other examples of
leaf nodes.
\begin{verbatim}
>>> exp(1)
E
>>> exp(1).args
()
>>> x.args
()
\end{verbatim}
\end{quote}
\end{solution}
\question The first
thing I tried after seeing Table 2 (simplication functions) did not work:

\begin{verbatim}
>>> trigsimp (exp( Matrix(2, 2, [0, -y, y, 0])) )
\end{verbatim}
fails to recognize cos and
sin. Am I expecting too much?
\begin{solution}
  This indeed does not work. The implementation in \verb|trigsimp| primarily
  thus far has focused on transforming trigonometric functions into other
  trigonometric functions. The ability to simplify complex exponentials is
  something that we would like to work.
  \href{https://github.com/sympy/sympy/issues/11459}{Issue 11459} in our
  public issue tracker tracks this feature.
\end{solution}
\question Section 3.6: are eigenvalues and singular
values included? If not, why not?
\begin{solution}
Yes, they are included.  The second example in that section addresses the computation of
eigenvalues.  Singular values can be computed with
\texttt{A.singular\_values()}. We have not included this example, as the
singular value expressions for our example matrix \texttt{A} are quite large,
but we have added ``singular values'' to the list of features in the second
paragraph of the section.
\end{solution}
\question Like one of the referees, I expected to
see MPFR mentioned in Section 4.1, at least to mention the pros and cons and
say why it isn't used.
\begin{solution}
  % TODO
\end{solution}
\question Section 4.1: please state whether the syntax for
functions in mpmath is identical, or not, to that in Sympy.
\begin{solution}
The mpmath library is not a SymPy submodule, but a separate library,
that should be clear for a reader from the text.  From that, we believe,
it should obvious that in general syntax (i.e. names for special
functions, order of their arguments, etc) will be different, just
as for any other external library.
\end{solution}
\question Unless I have
missed something, a weakness of the paper is that speed is mentioned only
twice, on lines 496 and 666. My assumption is that SymPy is slow compared with
its commercial competitors. Please comment on the speed issue, and not just in
the conclusions.
\begin{solution}
  % TODO
\end{solution}
\question Editors are needed for [20].
\begin{solution}
We have done this.
\end{solution}
\end{questions}

### 2016-08-17 matrices.tex
Some more for the editor comment 4

SymPy matrices support common symbolic linear algebra manipulations, including
matrix addition, multiplication, exponentiation, computing determinants,
solving linear systems, and computing inverses using LU decomposition, LDL
decomposition, Gauss-Jordan elimination, Cholesky decomposition, Moore-Penrose
pseudoinverse, and adjugate matrix.

>>>>

SymPy matrices support common symbolic linear algebra manipulations, including
matrix addition, multiplication, exponentiation, computing determinants,
solving linear systems, and computing inverses using LU decomposition, LDL
decomposition, Gauss-Jordan elimination, Cholesky decomposition, Moore-Penrose
pseudoinverse, singular values, and adjugate matrix.
